Brownian Dynein Model

### 2015-11-16 latex/derivation.tex
Add brief work on derivation.tex.
Finish-ish velocities. They are probably mostly right. If wrong, we can come back later and fix them without wasting effort, since the actual values are now defined as coefficients A, B, C, etc...

\begin{align}
  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
  &+ \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\dot{L}_f\\
\end{align}

@@

@@

@@

\textbf{REFORMAT!}

\begin{align}
  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}LL_s}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2\dot{L}_n}{4L_n^2LL_s}\dot{L}_n\\
  &\mp L_s\frac{\left(\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL^2_{n}} - \frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\\
  &\mp L_s\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}*\\
  &\frac{\left(\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L^2_{n}}
    - \frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{2L_{s}L_{n}}\right)}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
  A_{xf} &= \Bigg(\frac{-2L_s^2L_{f} - 2L_n^2L_{f} + 2L_t^2L_{f}}{4L_n^2LL_s} \mp L_s\frac{\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  &\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}\Bigg)\\
  B_{xn} &= \frac{L_n}{L}\\
  B_{xf} &= -\frac{L_f}{L}\\
  C_{xn} &= \\
  C_{xf} &= \\
  A_{yn} &= \\
  A_{yf} &= \\
  B_{yn} &= \frac{2L_n - \left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_n}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
  B_{yf} &= \frac{\left(\frac{L^2+L_n^2-L_f^2}{L}\right)\left(\frac{L_f}{L}\right)}{2\sqrt{L_n^2 - \left(\frac{L^2+L_n^2-L_f^2}{2L}\right)^2}}\\
  C_{yn} &= \\
  C_{yf} &= \\
\end{align}

@@

>>>>

\begin{align}
  \dot{X}_{nm} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
  &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\dot{L}_n\\
  &\Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\dot{L}_f\\
    %% &+ \Bigg(\frac{-L_s^2L_{f} - L_n^2L_{f} + L_t^2L_{f}}{2L_n^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}*\\
  %% &\left(-\frac{-2L_fL^2 - 2L^2L_{f} + 4L_{f}^3}{2LL_{n}}\right)\Bigg)\dot{L}_f\\
\end{align}

@@

\begin{align}
    \dot{Y}_{nm} &=
    \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
    &L_s\frac{-2\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^3} + \frac{4L_n^3 + 4L_sL_n - 4L_nL_t^2}{4L_s^2L_n^2}}{2\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}}\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Bigg)\dot{L}_n\\
    + &\Bigg(\frac{\frac{4L_f^3 - 4L^2L_f - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\\
    \pm &\left(\frac{-L_sL_{f}}{LL_{n}}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}}\Bigg)\dot{L}_f\\
\end{align}

@@

\begin{align}
  \dot{X}_{fm} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
  &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\dot{L}_f\\
  &\Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\dot{L}_n\\
    %% &+ \Bigg(\frac{-L_s^2L_n - L_f^2L_n + L_t^2L_n}{2L_f^2L} \mp L_s\frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}*\\
  %% &\left(-\frac{-2L_nL^2 - 2L^2L_n + 4L_n^3}{2LL_f}\right)\Bigg)\dot{L}_f\\
\end{align}

\begin{align}
    \dot{Y}_{fm} &=
    \Bigg(\left(-\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f^2} + 1\right)\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}} +\\
    &\frac{-2\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^3} + \frac{4L_f^3 + 4L^2L_f - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f} \pm\\
    &\left(-L_s\frac{L^2+L_f^2-L_n^2}{2LL_f^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}} \pm\\
    &L_s\frac{-2\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^3} + \frac{4L_f^3 + 4L_sL_f - 4L_fL_t^2}{4L_s^2L_f^2}}{2\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}}\frac{L^2+L_f^2-L_n^2}{2LL_f}\Bigg)\dot{L}_f\\
    + &\Bigg(\frac{\frac{4L_n^3 - 4L^2L_n - 4L_f^2L_n}{4L^2L_f^2}}{2\sqrt{1-\frac{L^4 + L_f^4 + L_n^4 + 2L^2L_f^2 - 2L^2L_n^2 - 2L_f^2L_n^2}{4L^2L_f^2}}}\frac{L_{s}^2+L_f^2-L_{t}^2}{2L_f}\\
    \pm &\left(\frac{-L_sL_n}{LL_f}\right)\sqrt{1-\frac{L_s^4 + L_f^4 + L_t^4 + 2L_sL_f^2 - 2L_s^2L_t^2 - 2L_f^2L_t^2}{4L_s^2L_f^2}}\Bigg)\dot{L}_n\\
\end{align}

@@

\subsection{Velocity Coefficients}
This subsection defines the coeffients to be used in further derivation.\\

@@

\begin{align}
  A_{xn} &= \Bigg(\frac{-L_s^2L^2 - L_n^2L^2 + L_t^2L^2 - L_s^2L_{n}^2 - L_n^2L_{n}^2 + L_t^2L_{n}^2 + L_s^2L_{f}^2 + L_n^2L_{f}^2 - L_t^2L_{f}^2}{{2L_n^{3}L}}\\
  &+ \frac{2L_nL^2 + 2L_s^2L_{n} + 4L_n^3 - 2L_t^2L_{n} - 2L_nL_{f}^2}{4L_n^2L}\\
  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_{n}^2}}}{2\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L_{n}^2}}}*\\
  &\left(L_s\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{4L^2L^3_{n}} - L_s\frac{2L_nL^2 + 2L^2L_{n} + 4L_{n}^3}{4L^2L_{n}^2}\right)\\
  &\mp \left(L_s\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
    - L_s\frac{2L_nL_{s}^2 + 2L_s^2L_{n} + 4L_{n}^3 - 2L_t^2L_{n} - 2L_nL_{t}^2}{4L_{s}^2L_{n}^2}\right)\\
    &\frac{\sqrt{1-\frac{L^4 + L_n^2L^2 - L_f^2L^2 + L^2L_{n}^2 + L_{n}^4 - L_f^2L_{n}^2 - L^2L_{f}^2 + L_n^2L_{f}^2 + L_{f}^4}{2LL_{n}}}}{2\sqrt{1-\frac{L_{s}^4 + L_n^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_{n}^2 + L_{n}^4 - L_t^2L_{n}^2 - L_s^2L_{t}^2 - L_n^2L_{t}^2 + L_{t}^4}{2L_{s}L_{n}}}}\Bigg)\\
  A_{xf} &= \Bigg(\frac{-2L_fL_s^2 - 2L_fL_n^2 + 2L_fL_t^2}{4LL_{n}^2}
  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}
  *\left(\frac{2L^2L_f - 2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L^2L_{n}^2}\right)\\
  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_n^2 - L^2L_f^2 + L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L^2L_{n}^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_n^2 - L_s^2L_t^2 L_n^2L^2 + L_n^4 - L_n^2L_f^2 - L_f^2L^2 - L_f^2L_n^2 + L_f^4}{4L_{s}^2L_{n}^2}\right)}}
  *\left(\frac{-2L_n^2L_f - 2L_fL^2 - 2L_fL_n^2 + 4L_f^3}{4L_{s}^2L_{n}^2}\right)\Bigg)\\
  B_{xn} &= \frac{L_n}{L}\\
  B_{xf} &= - \frac{L_f}{L}\\
\end{align}
\begin{align}
  C_{xn} &= \Bigg(\frac{-2L_nL_s^2 - 2L_nL_f^2 + 2L_nL_t^2}{4LL_f^2}
  \mp L_s\frac{\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}{2\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}
  *\left(\frac{2L^2L_n - 2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L^2L_f^2}\right)\\
  &\mp L_s\frac{\sqrt{1 - \left(\frac{L^4 + L^2L_f^2 - L^2L_n^2 + L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L^2L_f^2}\right)}}{2\sqrt{1-\left(\frac{L_s^4 + L_s^2L_f^2 - L_s^2L_t^2 L_f^2L^2 + L_f^4 - L_f^2L_n^2 - L_n^2L^2 - L_n^2L_f^2 + L_n^4}{4L_{s}^2L_f^2}\right)}}
  *\left(\frac{-2L_f^2L_n - 2L_nL^2 - 2L_nL_f^2 + 4L_n^3}{4L_{s}^2L_f^2}\right)\Bigg)\\
  C_{xf} &= \Bigg(\frac{-L_s^2L^2 - L_f^2L^2 + L_t^2L^2 - L_s^2L_f^2 - L_f^2L_f^2 + L_t^2L_f^2 + L_s^2L_n^2 + L_f^2L_n^2 - L_t^2L_n^2}{{2L_f^{3}L}}\\
  &+ \frac{2L_fL^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_n^2}{4L_f^2L}\\
  &\mp \frac{\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L_f^2}}}{2\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L_f^2}}}*\\
  &\left(L_s\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{4L^2L^3_{n}} - L_s\frac{2L_fL^2 + 2L^2L_f + 4L_f^3}{4L^2L_f^2}\right)\\
  &\mp \left(L_s\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{4L_{s}^2L^3_{n}}
    - L_s\frac{2L_fL_{s}^2 + 2L_s^2L_f + 4L_f^3 - 2L_t^2L_f - 2L_fL_{t}^2}{4L_{s}^2L_f^2}\right)\\
    &\frac{\sqrt{1-\frac{L^4 + L_f^2L^2 - L_n^2L^2 + L^2L_f^2 + L_f^4 - L_n^2L_f^2 - L^2L_n^2 + L_f^2L_n^2 + L_n^4}{2LL_f}}}{2\sqrt{1-\frac{L_{s}^4 + L_f^2L_{s}^2 - L_t^2L_{s}^2 + L_s^2L_f^2 + L_f^4 - L_t^2L_f^2 - L_s^2L_{t}^2 - L_f^2L_{t}^2 + L_{t}^4}{2L_{s}L_f}}}\Bigg)\\
\end{align}
\begin{align}
  A_{yn} &= \Bigg(\left(-\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_n^2} + 1\right)\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}} +\\
    &\frac{-2\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^3} + \frac{4L_n^3 + 4L^2L_n - 4L_n^2L_f}{4L^2L_n^2}}{2\sqrt{1-\frac{L^4 + L_n^4 + L_f^4 + 2L^2L_n^2 - 2L^2L_f^2 - 2L_n^2L_f^2}{4L^2L_n^2}}}\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}} \pm\\
    &\left(-L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}^2} + \frac{L_s\dot{L}_n}{L}\right)\sqrt{1-\frac{L_s^4 + L_n^4 + L_t^4 + 2L_sL_n^2 - 2L_s^2L_t^2 - 2L_n^2L_t^2}{4L_s^2L_n^2}} \pm\\
